---
title: "Homework 6"
author: "Cui Sitong (sc4636)"
date: "11/19/2019"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(leaps)
library(corrplot)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

```{r import data, message = FALSE}
bwt = read_csv("./data/birthweight.csv") %>%
  drop_na() %>% 
  mutate_at(c("babysex", "frace", "malform", "mrace"), as.factor) %>% 
  select(bwt, everything())
```

The data contained 4342 observations over 20 variables including baby's birth weight and 19 other possible predictors.

```{r}
lin_reg_1 = lm(bwt ~ babysex + mrace + gaweeks + momage + smoken + wtgain, data = bwt)

bwt = bwt %>% 
  add_predictions(lin_reg_1) %>% 
  add_residuals(lin_reg_1)

bwt %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .8, size = .5) +
  labs(
    title = "Residuals vs Fitted",
    x = "Fitted values",
    y = "Residuals"
  )
```

Model 1 is proposed in interest of exploring the relationship between mother's status and their baby's birth weight. Important predictors include mother's race, age, smoking status and weight gain during pregnancy. In addition, baby's gender and gestational age are included in the model since they are important confounders given previous studies. Other factors related to mother's status such as mother's height, menarch age and BMI are excluded since they are unlikely to be relevant. Also, mother's weight before pregnancy and at delivery are not considered since weight gain concludes the difference between them. In conclusion, 6 predictors are used in model 1 to predict baby's birthweight.

```{r}
cv_bwt = crossv_mc(bwt, nrow(bwt))

cv_bwt = 
  cv_bwt %>% 
  mutate(lin_reg_1  = map(train, ~lm(bwt ~ babysex + mrace + gaweeks + momage + smoken + wtgain, data = .x)),
         lin_reg_2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         lin_reg_3  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_1 = map2_dbl(lin_reg_1, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(lin_reg_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(lin_reg_3, test, ~rmse(model = .x, data = .y)))

cv_bwt %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

Among the three models, the last one has least RSME which means that model 3 gives relatively better prediction compared to model 1 and 2. This is reasonable as baby's head circumference and length indicate size of the baby which is highly associated with weight.

## Problem 2

```{r load data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r, warning = FALSE}
boot = weather_df %>% 
  bootstrap(n = 100) %>% 
  mutate(
    lin_reg = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(lin_reg, broom::tidy),
    r_sq = map(lin_reg, broom::glance)) %>% 
  select(-strap, -lin_reg) %>% 
  unnest(results, r_sq) %>% 
  select(.id, term, estimate, r.squared) %>% 
  mutate(term = recode(term, 
                       "(Intercept)" = "beta_0_hat",
                       "tmin" = "beta_1_hat")) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>% 
  mutate(log = log(beta_0_hat * beta_1_hat))

boot %>% ggplot(aes(x = log)) + 
  geom_density()
boot %>% ggplot(aes(x = r.squared)) + 
  geom_density()

boot %>% summarize(
  r_sq_025 = quantile(r.squared, .025),
  r_sq_975 = quantile(r.squared, .975),
  log_025 = quantile(log, .025),
  log_975 = quantile(log, .975)
)
```











